Fast Neural Machine Translation Implementation

### 2018-05-28 wnmt.2018/wnmt.tex
turn on timings
small numerical differences

This paper describes the submissions to the efficiency track for GPUs by members of the University of Edinburgh, Adam Mickiewicz University, Tilde and University of Alicante. We focus on efficient implementation of the recurrent deep-learning model as implemented in Amun, the fast inference engine for neural machine translation. We improve the performance with an efficient mini-batching algorithm and by fusing the softmax operation with the beam search algorithm.

@@

\begin{table}
\begin{center}
\begin{tabular}{|l|r|r|} \hline
		& Baseline	& Fused \\ \hline
\multicolumn{3}{|c|}{\emph{Beam size 1}}	\\ \hline	
Multiplication 	& 5.39 		& 5.38 (+0\%) \\ \hline
Add bias 	& 1.26		&  \\ 
Softmax 	& 1.69		& 2.07 (-86.6\%)\\
Beam search	& 12.53		&  \\ \hline
\multicolumn{3}{|c|}{\emph{Beam size 3}}	\\ \hline	
Multiplication 	& 14.18 	& 14.16 (+0\%) \\ \hline
Add bias 	& 3.76		&  \\ 
Softmax 	& 4.75		& 3.43 (-87.1\%)\\
Beam search	& 18.23		&  \\ \hline
\multicolumn{3}{|c|}{\emph{Beam size 9}}	\\ \hline	
Multiplication 	& 38.35 	& 38.42 (+0\%) \\ \hline
Add bias 	& 11.64		&  \\ 
Softmax 	& 14.4		& 17.5 (-72.1\%)\\
Beam search	& 36.7		&  \\ \hline
\end{tabular}
\end{center}
\caption{Time taken (sec) breakdown}
\label{tab:fused-breakdown}
\end{table}

>>>>

This paper describes the submissions to the efficiency track for GPUs by members of the University of Edinburgh, Adam Mickiewicz University, Tilde and University of Alicante. We focus on efficient implementation of the recurrent deep-learning model as implemented in Amun, the fast inference engine for neural machine translation. We improve the performance with an efficient mini-batching algorithm, and by fusing the softmax operation with the k-best extraction algorithm.

@@

\begin{table}
\begin{center}
\begin{tabular}{|l|r|r|} \hline
		& Baseline	& Fused \\ \hline
\multicolumn{3}{|c|}{\emph{Beam size 1}}	\\ \hline	
Multiplication 	& 5.39 		& 5.38 (+0\%) \\ \hline
Add bias 	& 1.26		&  \\ 
Softmax 	& 1.69		& 2.07 (-86.6\%)\\
K-best extr.	& 12.53		&  \\ \hline
\multicolumn{3}{|c|}{\emph{Beam size 3}}	\\ \hline	
Multiplication 	& 14.18 	& 14.16 (+0\%) \\ \hline
Add bias 	& 3.76		&  \\ 
Softmax 	& 4.75		& 3.43 (-87.1\%)\\
K-best extr.	& 18.23		&  \\ \hline
\multicolumn{3}{|c|}{\emph{Beam size 9}}	\\ \hline	
Multiplication 	& 38.35 	& 38.42 (+0\%) \\ \hline
Add bias 	& 11.64		&  \\ 
Softmax 	& 14.4		& 17.5 (-72.1\%)\\
K-best extr.	& 36.7		&  \\ \hline
\end{tabular}
\end{center}
\caption{Time taken (sec) breakdown}
\label{tab:fused-breakdown}
\end{table}
